---
title: "Dynamics of colistin resistance in chicken farms of the Mekong delta, Vietnam"
output:
  html_document:
    theme: cosmo
editor_options: 
  chunk_output_type: console
css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data

AMU is expressed either qualitative as presence (`TRUE`) / absence (`FALSE`)
variables
([here](https://raw.githubusercontent.com/viparc/colistin_resistance/master/data/viparc_qualitative.csv)),
or as g / kg of chicken
([here](https://raw.githubusercontent.com/viparc/colistin_resistance/master/data/viparc_quantitative.csv)).
These CSV files are are generated by this
[code](https://viparc.github.io/colistin_resistance/make_data.html). The first
data set can be downloaded as so:

```{r}
# install.packages("readr")
viparc_qualitative <- readr::read_csv("https://raw.githubusercontent.com/viparc/colistin_resistance/master/data/viparc_qualitative.csv",
                                      col_types = paste(c("cii", rep("l", 52), "il"), collapse = ""))
```

```{r include = FALSE}
nb_ab <- sum(grepl("_g", names(viparc_qualitative))) - 1
```

It contains `r nrow(viparc_qualitative)` weeks of observation (rows) and
`r ncol(viparc_qualitative)` variables (columns). The variables are

* **farm:** farm ID;
* **flock:** flock ID (in a given farm);
* **week:** week number (in a given flock of a given farm);
* **respiratory, ..., sudden_death:** presence (`TRUE`) / absence (`FALSE`) of 6 clinical signs in the flock;
* **amoxicillin_g, ..., unknown_g:** use (`TRUE`) or not (`FALSE`) of the `r nb_ab` antimicriobial used in the flock;
* **completed:** boolean informing whether the flock is done (`TRUE`) or still ongoing (`FALSE`);
* **nb_chicken:** total number of chicken in the farm;
* **sampling:** boolean informing whether there is feces sampling during the week (`TRUE`) or not (`FALSE`).

The second data set can be downloaded as so:

```{r}
# install.packages("readr")
viparc_quantitative <- readr::read_csv("https://raw.githubusercontent.com/viparc/colistin_resistance/master/data/viparc_quantitative.csv",
                                       col_types = paste(c("cii", rep("l", 6), rep("d", 45), "lildd"), collapse = ""))
```

```{r include = FALSE}
nb_ab <- sum(grepl("_g", names(viparc_quantitative))) - 1
```

It contains `r nrow(viparc_quantitative)` weeks of observation (rows) and
`r ncol(viparc_quantitative)` variables (columns). The variables are

* **farm:** farm ID;
* **flock:** flock ID (in a given farm);
* **week:** week number (in a given flock of a given farm);
* **respiratory, ..., sudden_death:** presence (`TRUE`) / absence (`FALSE`) of 6 clinical signs in the flock;
* **amoxicillin_g, ..., unknown_g:** mass, in g / kg of chicken, of the `r nb_ab` antimicriobial used in the flock;
* **completed:** boolean informing whether the flock is done (`TRUE`) or still ongoing (`FALSE`);
* **nb_chicken:** total number of chicken in the farm;
* **sampling:** boolean informing whether there is feces sampling during the week (`TRUE`) or not (`FALSE`);
* **individual_weight_kg:** average weight in kg of a chicken;
* **farm_weight_kg:** expected weight in kg of whole the chicken of the farm.